---
title: "graphic_description"
description: |
  Comparison between the weight and height of the genders.
author:
  - name: Emeline Derycke
    url: {}
date: 11-14-2020
categories:
  - "Data Sciences I"
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
SciViews::R
```

```{r}
data <- read("biometry", package = "BioDataScience")
```
I chose "biometry" as the dataset because it represents data on humans. Moreover it is the one we use the least. This is why I would like to make a comparison between the weight and height of the genders.

```{r}
a <-chart(data, ~ weight %fill=% gender) +
  geom_histogram(bins = 30) +
  ylab("Effectifs")

b <-chart(data, ~height %fill=% gender) +
  geom_histogram(bins = 30) +
  ylab("Effectifs")

combine_charts(list(a,b))
```

In general, men are heavier and taller than women.
Only the women have a weight of less than 60 kg and a height of less than 160cm but some men are in its slices there but it is only a small part.
